Analytic Light Curves in Reflected Light: \\% Phase Curves, Occultations, and Non-Lambertian Scattering

### 2020-05-14 tex/ms.tex
finished proof
fixed several typos in rT
fixed one more in rT
added new proof
added proof
new proof

@@

@@

        \frac{\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu + 2}{2}}

@@

        \mu, \nu \ \text{even}

@@

        \mathbb{k}_{\frac{\nu + 1}{2}}(b) \mathbb{M}_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}

@@

we may compute all higher order terms from the recurrence relations

@@

    \mathbb{k}_{j}(b) &= \frac{b^n b_c^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}

@@

    \hat{f}_0 &=

@@

The key to identifying the case corresponding to a given configuration is
to determine whether or not the limb of the occultor intersects the terminator
of the body, and if so, the points of intersection.
While we perform the integration in frame $\mathcal{F}'$, finding the points
of intersection with the terminator is easier if we temporarily switch to
the frame $\mathcal{F}''$, in which the terminator
is parallel to the $x''$-axis.
In this frame, the equations defining the terminator and the limb of the
occultor are, respectively,
%
\begin{proof}{}
    y''_1(x'') & = b \sqrt{1 - x''^2}
    \nonumber                                               \\
    y''_2(x'') & = y''_o \pm \sqrt{r_o^2 - (x'' - x''_o)^2}
\end{proof}
%
where
%
\begin{proof}{}
    x''_o = b_o\sin\theta'
    \nonumber \\
    y''_o = b_o\cos\theta'
\end{proof}
%
are the coordinates of the occultor in $\mathcal{F}''$.
%
We wish to find the vector of $N$ points
$\mathbf{x''} = \left(x_0, x_1, {\cdot\cdot\cdot}, x_{N-1}\right)^\top$
for which
$y''_1(x_n'') - y''_2(x_n'') = 0$. Following \citet{Luger2017}, we may
express this condition as the quartic equation
%
\begin{proof}{}
    \label{eq:quartic}
    A {x''}^4 + B {x''}^3 + C {x''}^2 + D {x''} + E = 0
\end{proof}
%
with coefficients
%
\begin{proof}{}
    \label{eq:quartic-coeffs}
    A &= (1 - b^2)^2
    \nonumber \\
    B &= -4 x''_o (1 - b^2)
    \nonumber \\
    C &= -2 \bigg(
    b^4
    + r_o^2
    - 3 {x''_o}^2
    - {y''_o}^2
    - b^2 \big(1 + r_o^2 - {x''_o}^2 + {y''_o}^2\big)
    \bigg)
    \nonumber \\
    D &= -4 x''_o (b^2 - r_o^2 + {x''_o}^2 + {y''_o}^2)
    \nonumber \\
    E &=
    b^4
    - 2 b^2 \big(r_o^2 - {x''_o}^2 + {y''_o}^2\big)
    + \big(r_o^2 - {x''_o}^2 - {y''_o}^2\big)^2
    \quad.
\end{proof}
%
Although closed-form solutions to quartic equations exist
\citep[see, e.g.,][who solve for the area of overlap between two ellipses
    analytically]{Hughes2011}, they are prone to significant numerical
instabilities. Instead, we solve for the roots of the quartic
numerically by casting it
as an eigenvalue problem \citep[e.g.,][]{Edelman1995} and polish the
results with a few iterations of Newton's method. We find that this is
reasonably computationally efficient and
yields roots with precision within a couple orders of magnitude of machine
epsilon (see \S\ref{sec:performance}).

@@

\subsection{Cases 1--5}
\label{sec:cases-easy}
%
Cases 1--5 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve. In particular, we can use the original emitted
light solution from \citet{Luger2019}, provided we weight the map by our
polynomial illumination function:
%
\begin{proof}{}
    \label{eq:fI}
    f_I &=
    \sTe(b_o, r_o)
    \mathbf{A_2}
    \mathbf{I}(b, \theta', r_s)
    \mathbf{A_1}
    \mathbf{R}'(x_o, y_o)
    \mathbf{R}(\text{I}, \Lambda, \Theta)
    \mathbf{y}
    \quad,
\end{proof}
%
where $\sTe(b_o, r_o)$ is the emitted light solution vector
\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
measure from a body whose surface map is weighted by the illumination function
$\mathbf{I}(b, \theta', r_s)$ during an occultation. Note that this is not
necessarily the \emph{observed} flux, since this may include the unphysical
negative contribution from the nightside. We must compute the actual
observed flux on a case-by-case basis.

Case 1 corresponds to any complete occultation of the body
($b_o \le r_o - 1$), so the solution for the flux is trivial:
%
\begin{align}
    \label{eq:f1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 corresponds to occultations in which the occultor blocks \emph{all} of
the dayside of the body and \emph{some} of the nightside. In this
configuration, the unocculted part of the disk consists only of nightside, so
the solution is again trivial:
%
\begin{align}{}
    \label{eq:f2}
    f_2 = 0
    \quad.
\end{align}
%
Conversely, case 3 corresponds to occultations in which the occultor blocks
\emph{all} of the nightside of the body and \emph{some} of the dayside.
Since the visible portion of the disk consists only of dayside, we can
simply use the weighted solution in emitted light
(Equation~\ref{eq:fI}):
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = f_I
\end{proof}
%
Case 4 involves any occultation in which the occultor blocks \emph{only} the
nightside of the body (regardless of whether or not it intersects with the
limb of the body). Since the nightside intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:f4}
    f_2 = f_0
    \quad.
\end{align}
%
Finally, case 5 involves any occultation in which the occultor blocks
\emph{only} the dayside of the body (regardless of whether or not it
intersects with the limb). We first compute the illumination-weighted flux
$f_I$ as above, then negate the unphysical nightside contribution
using Equation~(\ref{eq:f0hat}):
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_I - \hat{f}_0
    \quad.
\end{proof}

@@

Case 6 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $\mathcal{P}$, $\mathcal{Q}$, and $\mathcal{T}$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 7--10 involve two points of intersection between the occultor limb and
the terminator.
%
Cases 7 and 8 correspond to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. In case 7 a lens-shaped region is formed by the
intersection of the occultor limb and the terminator on the
\emph{nightside}, while in case 8 this region is formed on the \emph{dayside}.
%
In case 7, we begin by computing the
flux over the unocculted region, $f_I$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f7}
    f_7 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Case 8, on the other hand, is topologically equivalent to case 6, since
the integration region consists of occulted dayside:
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 9 and 10 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 9
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{proof}{}
    \label{eq:f9}
    f_9 = f_I - f_S
    \quad.
\end{proof}
%
Conversely, case 10 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{proof}{}
    \label{eq:f10}
    f_{10} = f_S
    \quad.
\end{proof}
%

@@

Cases 11--14 correspond to (rare) configurations involving three
or four roots to Equation~\ref{eq:quartic} and are
illustrated in Figure~\ref{fig:pathological}. All four involve integration over
two disjoint regions (see the figure).
%
Cases 11 and 12 involve three points of intersection between the terminator
and the occultor limb. In case 11, the regions of integration $S_1$ and
$S_2$ are the
occulted portion of the dayside, so the solution is similar to
that of cases 6 and 8:
%
\begin{proof}{}
    \label{eq:f11}
    f_{11} = f_0 - (f_{S_1} + f_{S_2})
    \quad,
\end{proof}
%
where $f_{S_1}$ and $f_{S_2}$ are computed from Equation~(\ref{eq:fS}) for
each of the integration regions. Conversely, in case 12 the two regions
are the occulted portion of the nightside, so the solution is similar to that
of case 7:
%
\begin{proof}{}
    \label{eq:f12}
    f_{12} = f_I - \big(\hat{f}_0 - (f_{S_1} + f_{S_2})\big)
    \quad,
\end{proof}
%
Finally, cases 13 and 14 involve four points of intersection between the
terminator and the occultor limb. The regions of integration in case 13 are
the visible portion of the nightside, so this case is equivalent to case 9:
%
\begin{proof}{}
    \label{eq:f13}
    f_{13} = f_I - (f_{S_1} + f_{S_2})
    \quad.
\end{proof}
%
Conversely, the regions of integration in case 14 are the
visible portion of the dayside, so this case is equivalent to case 10:
%
\begin{proof}{}
    \label{eq:f14}
    f_{14} = f_{S_1} + f_{S_2}
    \quad.
\end{proof}
%

@@

@@

\subsection{The integral along the occultor limb, $\pT$}
\label{sec:pT}
%
In this section we present a solution to Equation~(\ref{eq:pT}). The first
order of business is to derive expressions for the integration limits
$\pmb{\phi}$. Depending on the integration case, these limits will correspond
to the point of intersection between the limb of the occultor and the
limb of the occulted body and/or the point of intersection between the limb
of the occultor and the terminator of the occulted body.
The former is given by
\citep[c.f. Equation~24 in][]{Luger2019}
%
\begin{align}
    \phi_0 & =
    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
    \quad,
\end{align}
%
where the sign is chosen such that the point
$(r_o\cos\phi_0, b_o + r_o\sin\phi_0)$ is on the dayside of the occulted body,
and the latter (of which there may be multiple) is given by
%
% Introduce the function
% %
% \begin{proof}{}
%     \textrm{\faAdjust}(x, y) &=
%     \begin{cases}
%         \textrm{\faCircleO} & \qquad -x \sin\theta' + y\cos\theta' \ge b \sqrt{1 - (x\cos\theta' + y\sin\theta') ^ 2}
%         \\
%         \textrm{\faCircle}  & \qquad \text{otherwise}
%     \end{cases}
% \end{proof}
% %
% which returns \faCircleO\ if point $(x, y)$ is on the dayside of the body and
% \faCircle\ if it is on the nightside.
%
%
\begin{align}
    \pmb{\phi_1} & =
    \theta' +
    \atantwo
    \left(b\sqrt{1 - {\mathbf{x''}}^2 - y''_o}, \mathbf{x''} - x''_o\right)
    \quad
\end{align}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
These angles are then wrapped to the range $[0, 2\pi)$
and sorted into the vector $\pmb{\phi}$ such that
the integration is always performed in a counter-clockwise sense about
the center of the integration region.
%
The left panel in Figure~\ref{fig:geometry} shows a configuration in which
the lower integration limit $\phi_0 = 158.2^\circ$ corresponds to the
point of intersection between the limbs of the two bodies and the upper
integration limit $\phi_1 = 223.3^\circ$ corresponds to the
limb-terminator intersection. Both angles are measured counter-clockwise
from the line $x' = b_o$.

@@

@@

                    \frac{\mu + 2}{2},

@@

                         & \qquad \quad

@@

    \mathbf{x}_{u + w + i}

>>>>

\begin{proof}{illumination}

@@

\begin{proof}{PhaseCurve}

@@

        \frac{\left(1 - b^{\frac{\nu + 2}{2}}\right)}{2}
        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu}{2}}

@@

        \frac{\mu}{2} \ \text{even}

@@

        \mathbb{k}_{\frac{\nu - 1}{2}}(b) \mathbb{M}_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}}
        \frac{\mu - 1}{2} \ \text{even}

@@

we may compute all the required higher order terms from the recurrence relations
\begin{proof}{PhaseCurve}

@@

    \mathbb{k}_{j}(b) &= \frac{b^{j-1} b_c^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}

@@

    \hat{f}_0 & =

@@

The key to identifying the case corresponding to a given configuration is
to determine whether or not the limb of the occultor intersects the terminator
of the body, and if so, the points of intersection.
While we perform the integration in frame $\mathcal{F}'$, finding the points
of intersection with the terminator is easier if we temporarily switch to
the frame $\mathcal{F}''$, in which the terminator
is parallel to the $x''$-axis.
In this frame, the equations defining the terminator and the limb of the
occultor are, respectively,
%
\begin{proof}{quartic}
    y''_1(x'') & = b \sqrt{1 - x''^2}
    \nonumber                                               \\
    y''_2(x'') & = y''_o \pm \sqrt{r_o^2 - (x'' - x''_o)^2}
\end{proof}
%
where
%
\begin{proof}{quartic}
    x''_o = b_o\sin\theta'
    \nonumber \\
    y''_o = b_o\cos\theta'
\end{proof}
%
are the coordinates of the occultor in $\mathcal{F}''$.
%
We wish to find the vector of $N$ points
$\mathbf{x''} = \left(x_0, x_1, {\cdot\cdot\cdot}, x_{N-1}\right)^\top$
for which
$y''_1(x_n'') - y''_2(x_n'') = 0$. Following \citet{Luger2017}, we may
express this condition as the quartic equation
%
\begin{proof}{quartic}
    \label{eq:quartic}
    A {x''}^4 + B {x''}^3 + C {x''}^2 + D {x''} + E = 0
\end{proof}
%
with coefficients
%
\begin{proof}{quartic}
    \label{eq:quartic-coeffs}
    A &= (1 - b^2)^2
    \nonumber \\
    B &= -4 x''_o (1 - b^2)
    \nonumber \\
    C &= -2 \bigg(
    b^4
    + r_o^2
    - 3 {x''_o}^2
    - {y''_o}^2
    - b^2 \big(1 + r_o^2 - {x''_o}^2 + {y''_o}^2\big)
    \bigg)
    \nonumber \\
    D &= -4 x''_o (b^2 - r_o^2 + {x''_o}^2 + {y''_o}^2)
    \nonumber \\
    E &=
    b^4
    - 2 b^2 \big(r_o^2 - {x''_o}^2 + {y''_o}^2\big)
    + \big(r_o^2 - {x''_o}^2 - {y''_o}^2\big)^2
    \quad.
\end{proof}
%
Although closed-form solutions to quartic equations exist
\citep[see, e.g.,][who solve for the area of overlap between two ellipses
    analytically]{Hughes2011}, they are prone to significant numerical
instabilities. Instead, we solve for the roots of the quartic
numerically by casting it
as an eigenvalue problem \citep[e.g.,][]{Edelman1995} and polish the
results with a few iterations of Newton's method. We find that this is
reasonably computationally efficient and
yields roots with precision within a couple orders of magnitude of machine
epsilon (see \S\ref{sec:performance}).

@@

\subsection{Cases 1--5}
\label{sec:cases-easy}
%
Cases 1--5 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve. In particular, we can use the original emitted
light solution from \citet{Luger2019}, provided we weight the map by our
polynomial illumination function:
%
\begin{align}
    \label{eq:fI}
    f_I & =
    \sTe(b_o, r_o)
    \mathbf{A_2}
    \mathbf{I}(b, \theta', r_s)
    \mathbf{A_1}
    \mathbf{R}'(x_o, y_o)
    \mathbf{R}(\text{I}, \Lambda, \Theta)
    \mathbf{y}
    \quad,
\end{align}
%
where $\sTe(b_o, r_o)$ is the emitted light solution vector
\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
measure from a body whose surface map is weighted by the illumination function
$\mathbf{I}(b, \theta', r_s)$ during an occultation. Note that this is not
necessarily the \emph{observed} flux, since this may include the unphysical
negative contribution from the nightside. We must compute the actual
observed flux on a case-by-case basis.

Case 1 corresponds to any complete occultation of the body
($b_o \le r_o - 1$), so the solution for the flux is trivial:
%
\begin{align}
    \label{eq:f1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 corresponds to occultations in which the occultor blocks \emph{all} of
the dayside of the body and \emph{some} of the nightside. In this
configuration, the unocculted part of the disk consists only of nightside, so
the solution is again trivial:
%
\begin{align}{}
    \label{eq:f2}
    f_2 = 0
    \quad.
\end{align}
%
Conversely, case 3 corresponds to occultations in which the occultor blocks
\emph{all} of the nightside of the body and \emph{some} of the dayside.
Since the visible portion of the disk consists only of dayside, we can
simply use the weighted solution in emitted light
(Equation~\ref{eq:fI}):
%
\begin{align}
    \label{eq:f3}
    f_3 = f_I
\end{align}
%
Case 4 involves any occultation in which the occultor blocks \emph{only} the
nightside of the body (regardless of whether or not it intersects with the
limb of the body). Since the nightside intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:f4}
    f_4 = f_0
    \quad.
\end{align}
%
Finally, case 5 involves any occultation in which the occultor blocks
\emph{only} the dayside of the body (regardless of whether or not it
intersects with the limb). We first compute the illumination-weighted flux
$f_I$ as above, then negate the unphysical nightside contribution
using Equation~(\ref{eq:f0hat}):
%
\begin{align}
    \label{eq:f5}
    f_5 = f_I - \hat{f}_0
    \quad.
\end{align}

@@

Case 6 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $\mathcal{P}$, $\mathcal{Q}$, and $\mathcal{T}$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{align}
    \label{eq:f6}
    f_6 = f_0 - f_S
    \quad.
\end{align}
%
Cases 7--10 involve two points of intersection between the occultor limb and
the terminator.
%
Cases 7 and 8 correspond to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. In case 7 a lens-shaped region is formed by the
intersection of the occultor limb and the terminator on the
\emph{nightside}, while in case 8 this region is formed on the \emph{dayside}.
%
In case 7, we begin by computing the
flux over the unocculted region, $f_I$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{align}
    \label{eq:f7}
    f_7 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{align}
%
Case 8, on the other hand, is equivalent to case 6, since
the integration region consists of occulted dayside:
%
\begin{align}
    \label{eq:f8}
    f_8 = f_0 - f_S
    \quad.
\end{align}
%
Cases 9 and 10 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 9
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{align}
    \label{eq:f9}
    f_9 = f_I - f_S
    \quad.
\end{align}
%
Conversely, case 10 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{align}
    \label{eq:f10}
    f_{10} = f_S
    \quad.
\end{align}
%

@@

Cases 11--14 correspond to (rare) configurations involving three
or four roots to Equation~(\ref{eq:quartic}) and are
illustrated in Figure~\ref{fig:pathological}. All four involve integration over
two disjoint regions (see the figure).
%
Cases 11 and 12 involve three points of intersection between the terminator
and the occultor limb. In case 11, the regions of integration $S_1$ and
$S_2$ are the
occulted portion of the dayside, so the solution is similar to
that of cases 6 and 8:
%
\begin{align}
    \label{eq:f11}
    f_{11} = f_0 - (f_{S_1} + f_{S_2})
    \quad,
\end{align}
%
where $f_{S_1}$ and $f_{S_2}$ are computed from Equation~(\ref{eq:fS}) for
each of the integration regions. Conversely, in case 12 the two regions
are the occulted portion of the nightside, so the solution is similar to that
of case 7:
%
\begin{align}
    \label{eq:f12}
    f_{12} = f_I - \big(\hat{f}_0 - (f_{S_1} + f_{S_2})\big)
    \quad,
\end{align}
%
Finally, cases 13 and 14 involve four points of intersection between the
terminator and the occultor limb. The regions of integration in case 13 are
the visible portion of the nightside, so this case is equivalent to case 9:
%
\begin{align}
    \label{eq:f13}
    f_{13} = f_I - (f_{S_1} + f_{S_2})
    \quad.
\end{align}
%
Conversely, the regions of integration in case 14 are the
visible portion of the dayside, so this case is equivalent to case 10:
%
\begin{align}
    \label{eq:f14}
    f_{14} = f_{S_1} + f_{S_2}
    \quad.
\end{align}
%

@@

\begin{proof}{Greens}

@@

\subsection{The integral along the occultor limb, $\pT$}
\label{sec:pT}
%
In this section we present a solution to Equation~(\ref{eq:pT}). The first
order of business is to derive expressions for the integration limits
$\pmb{\phi}$. Depending on the integration case, these limits will correspond
to the point of intersection between the limb of the occultor and the
limb of the occulted body and/or the point of intersection between the limb
of the occultor and the terminator of the occulted body.
The former is given by
\citep[c.f. Equation~24 in][]{Luger2019}
%
\begin{proof}{pT}
    \phi_0 & =
    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
    \quad,
\end{proof}
%
where the sign is chosen such that the point
$(r_o\cos\phi_0, b_o + r_o\sin\phi_0)$ is on the dayside of the occulted body,
and the latter (of which there may be multiple) is given by
%
% Introduce the function
% %
% \begin{proof}{}
%     \textrm{\faAdjust}(x, y) &=
%     \begin{cases}
%         \textrm{\faCircleO} & \qquad -x \sin\theta' + y\cos\theta' \ge b \sqrt{1 - (x\cos\theta' + y\sin\theta') ^ 2}
%         \\
%         \textrm{\faCircle}  & \qquad \text{otherwise}
%     \end{cases}
% \end{proof}
% %
% which returns \faCircleO\ if point $(x, y)$ is on the dayside of the body and
% \faCircle\ if it is on the nightside.
%
%
\begin{proof}{pT}
    \pmb{\phi_1} & =
    \theta' +
    \atantwo
    \left(b\sqrt{1 - {\mathbf{x''}}^2} - y''_o, \mathbf{x''} - x''_o\right)
    \quad
\end{proof}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
These angles are then wrapped to the range $[0, 2\pi)$
and sorted into the vector $\pmb{\phi}$ such that
the integration is always performed in a counter-clockwise sense about
the center of the integration region.
%
The left panel in Figure~\ref{fig:geometry} shows a configuration in which
the lower integration limit $\phi_0 = 158.2^\circ$ corresponds to the
point of intersection between the limbs of the two bodies and the upper
integration limit $\phi_1 = 223.3^\circ$ corresponds to the
limb-terminator intersection. Both angles are measured counter-clockwise
from the line $x' = b_o$.

@@

\begin{proof}{pT}

@@

                    \frac{\mu + 2}{4},

@@

                         & \qquad \quad  \enspace

@@

    x_{u + w + i}
